Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Spacing and line widths
Commas and the like

\section{The Constraint Models}
The schedules are produced in 4 stages. The first stage produces a schedule that respects criteria 1, 4, 11 and 12 and minimises criteria 10 (boat changes). The second stage constructs a schedule that respects criteria 1,4,11,12 again and has criteria 10 as a hard constraint generated from first stage and minimises criteria 6 (balance). This results in a schedule that attempts to minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.  The final stage, stage 4, orients skippers within matches to address criteria 2, 3, 5 and 8.

>>>>

\section{The Constraint Models}

The schedules are produced in four stages. The first stage produces a schedule
that respects criteria 1, 4, 11 and 12, and minimises criteria 10 (boat
changes). The second stage constructs a schedule that respects criteria 1, 4,
11, 12 (again), has criteria 10 as a hard constraint generated from first
stage, and minimises criteria 6 (balance). This results in a schedule that
attempts to minimise boat changes \emph{and} balance. The third stage satisfies
criteria 9, and is a simple translation of the schedule produced in stage 2.
The final stage, orients skippers within matches to address criteria 2, 3, 5
and 8.
